What's hot and what's not:\\Windowing developer topic analysis

### 2009-04-08 lda-paper.tex
uhu

\title{Windowed Developer Topic Analysis}

@@

During different periods, developers focus on different topics and
different tasks during development. Stake-holders, such as managers, who are
not directly involved with the project's development might have less awareness of the
project and the topics and tasks that the developers have focussed on.
Imagine the scenario where a manager is trying to discover where all the
developers' effort went after features have not been implemented because the
developers unexpectedly had to deal with issues orthogonal to these
features.  We propose to help stake-holders understand the topics of
development by extracting topics from the descriptions of changes that
programmers provide when they make commits.  We leverage topic analysis
tools such as Latent Dirichlet Allocation (LDA) or Latent Semantic Indexing
(LSI) to analyze periods, such as months, within a project's lifetime,
whereas previous work applied LDA and LSI to to a project's entire lifetime.  These
tools associate descriptions with independent topics extracted from these
descriptions.  
We propose a visualization of changing development topics
over time that allows us to see the evolving stream of topics of development
occurring over time. We demonstrate that windowed topic analysis offers
benefits over entire lifetime topic analysis because of the
independence of topics between windows.

@@

Topic analysis, with respect to Software Control Systems (SCSs) like
CVS, Subversion, Git etc., is potentially valuable as it has many uses
for various stake-holders and uses.
Imagine a
development team has agreed to implement some features at the start of
an iteration. By the end of the iteration only some of the agreed upon
features are implemented. The developers swear they were focusing
solely on the features agreed upon. Topic analysis could help by
teasing out the distinct topics or focusses of the developers. Perhaps
the developers had to deal with issues.
Developers might have grouped those orthogonal changes into
one of the features they were working on, thus when asked about how
their time was spent the orthogonal changes would not be covered. This
is what we hope that windowed topic analysis can uncover. If windowed
topic analysis can discover important but overlooked topics, it can
help both developers and managers. Developer can see a
summary of what worked on, and managers can development.

@@

\begin{table*}
\centering
\begin{tabular}{|cc|l|}
\hline
2000 &  Jul &      chmod \\
2000 &  Sep &      fixes benchmark logging Win32 \\
2000 &  Nov &      fixes insert\_multi\_value \\
2001 &  Jan &      fixes Innobase Cleanups auto-union \\
2001 &  Mar &      bugfix logging  TEMPORARY  \\
\hline         
2001 &  Jul &      TABLES update Allow LOCK \\

2001 &  Aug &      TABLES row version \\
\hline         
2001 &  Sep &      update checksum merge \\
2001 &  Oct &      fixed fix \\
2001 &  Dec &      HPUX SCO fix \\
\hline         
2002 &  Feb &      net buffer length  max\_allowed\_packet \\
2002 &  Mar &      small buf fix  \\
\hline         
2002 &  May &      [popular] fix SCO OSF1 table\_name \\
2002 &  Nov &      HPUX11 compiler HP \\
\hline         
2003 &  Feb &      Linux errno   \\
2003 &  Mar &      alarm bookmark bug \\
\hline         
2003 &  Sep &      Auto logging merge windows distribution fix 64-bit 4.0 Cleanup \\
\hline
\end{tabular}
\caption{Sub-sampled topics from MySQL 3.23, some with continuous topics, these tokens were pulled from LDA topic. Each token is a summary of one LDA generated topic from MySQL 3.23 commit logs.}
\label{tab:portability}
\end{table*}

>>>>

%\title{Windowed Developer Topic Analysis}
\title{What's hot and what's not:\\Windowing developer topic analysis}

@@

% During different periods, developers focus on different topics and
% different tasks during development. Stake-holders, such as managers, who are
% not directly involved with the project's development might have less awareness of the
% project and the topics and tasks that the developers have focussed on.
% Imagine the scenario where a manager is trying to discover where all the
% developers' effort went after features have not been implemented because the
% developers unexpectedly had to deal with issues orthogonal to these
% features.  We propose to help stake-holders understand the topics of
% development by extracting topics from the descriptions of changes that
% programmers provide when they make commits.  We leverage topic analysis
% tools such as Latent Dirichlet Allocation (LDA) or Latent Semantic Indexing
% (LSI) to analyze periods, such as months, within a project's lifetime,
% whereas previous work applied LDA and LSI to to a project's entire lifetime.  These
% tools associate descriptions with independent topics extracted from these
% descriptions.  
% We propose a visualization of changing development topics
% over time that allows us to see the evolving stream of topics of development
% occurring over time. We demonstrate that windowed topic analysis offers
% benefits over entire lifetime topic analysis because of the
% independence of topics between windows.

As development on a software project progresses, developers will naturally
shift their focus between different topics and tasks many times.  Managers
and newcomer developers often seek simple ways of understanding what tasks
have recently been worked on and how much effort has gone into each; for
example, a manager might wonder what unexpected tasks occupied their team's
attention during a period when they were supposed to have been implementing
a set of new features.  Tools such as Latent Dirichlet Allocation (LDA) and
Latent Semantic Indexing (LSI) can be used to analyze check-in comments
over the entire lifetime of a project, and previous work on developer topic
analysis has leveraged these tools to associate commit log comments with
independent topics extracted from these commit log comments.  In this work, we use
LDA and LSI to analyze periods, such as months, within a project's lifetime
to create a time-windowed model of changing development topics.  We propose
a visualization of this model that allows us to explore the evolving stream
of topics of development occurring over time, and we demonstrate that
windowed topic analysis offers strong advantages over entire lifetime topic
analysis because of the independence of topics between windows.

@@

Topic analysis, with respect to Software Control Systems (SCSs) like
CVS, Subversion, Git etc., is potentially valuable as it has many uses
for various stakeholders and uses.
Imagine a
development team has agreed to implement some features at the start of
an iteration. By the end of the iteration only some of the agreed upon
features are implemented. The developers swear they were focusing
solely on the features agreed upon. Topic analysis could help by
teasing out the distinct topics or focusses of the developers. Perhaps
the developers had to deal with issues.
Developers might have grouped those orthogonal changes into
one of the features they were working on, thus when asked about how
their time was spent the orthogonal changes would not be covered. This
is what we hope that windowed topic analysis can uncover. If windowed
topic analysis can discover important but overlooked topics, it can
help both developers and managers. Developer can see a
summary of what worked on, and managers can development.

@@

\begin{table}
\centering
\begin{tabular}{|cc|l|}
\hline
2000 &  Jul &      chmod \\
2000 &  Sep &      fixes benchmark logging Win32 \\
2000 &  Nov &      fixes insert\_multi\_value \\
2001 &  Jan &      fixes Innobase Cleanups auto-union \\
2001 &  Mar &      bugfix logging  TEMPORARY  \\
\hline         
2001 &  Jul &      TABLES update Allow LOCK \\

2001 &  Aug &      TABLES row version \\
\hline         
2001 &  Sep &      update checksum merge \\
% 2001 &  Oct &      fixed fix \\
% 2001 &  Dec &      HPUX SCO fix \\
% \hline         
% 2002 &  Feb &      net buffer length  max\_allowed\_packet \\
% 2002 &  Mar &      small buf fix  \\
% \hline         
% 2002 &  May &      [popular] fix SCO OSF1 table\_name \\
% 2002 &  Nov &      HPUX11 compiler HP \\
% \hline         
% 2003 &  Feb &      Linux errno   \\
% 2003 &  Mar &      alarm bookmark bug \\
% \hline         
% 2003 &  Sep &      Auto logging merge windows distribution fix 64-bit 4.0 Cleanup \\
\hline
\end{tabular}
\caption{Sub-sampled topics from MySQL 3.23, some with continuous topics, these tokens were pulled from LDA topic. Each token is a summary of one LDA generated topic from MySQL 3.23 commit logs.}
\label{tab:portability}
\end{table}
